Scottish Child Poverty Briefing Plots

### 2024-06-19 minos/outcomes/ChildPovReduction_Combined.Rmd
Changed the inequality plots to use income_quint summaries from the together batch

  data <- replace_na(data, list(num_priority_groups=0))

@@

```{r "inequality_plots", include=FALSE}
inequality_plots <- function(summary_group, scen.list) {

@@

  # Combine the data
  data_combined <- data %>%
    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))

@@

  # Aggregate data
  agg_data <- data %>%
    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention')) %>%
    group_by(year, income_quintile, scenario) %>%
    summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
    spread(scenario, mean_SF_12) %>%
    mutate(difference = Intervention - Baseline)

@@

```{r}
inequality_plots(summary_group = 'whole_pop',
                 scen.list = scen.list.rel)
```

@@

```{r}
inequality_plots(summary_group = 'families',
                 scen.list = scen.list.rel)
```

@@

```{r}
inequality_plots(summary_group = 'whole_pop',
                 scen.list = scen.list.abs)
```

@@

```{r}
inequality_plots(summary_group = 'families',
                 scen.list = scen.list.abs)
```

>>>>

  #data <- replace_na(data, list(num_priority_groups=0))

@@

```{r "inequality_plots", include=FALSE}
# inequality_plots <- function(summary_group, scen.list) {
#   
#   tit <- ' '
#   if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
#   if (summary_group == 'families') { tit <- 'Families' }
#   
#   summary_group <- paste0(summary_group, '_income_quint')
#   
#   data <- do.call(rbind, generate_df_list(summary_group, scen.list))
#   
#   data$income_quintile <- factor(data$income_quintile)
#   
#   # Combine the data
#   data_combined <- data %>%
#     mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))
#   
#   p1 <- ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
#     geom_smooth(alpha = 0.7) +
#     scale_color_manual(name = "Income Quintile", 
#                        values = c("red", "blue", "green", "orange", "purple")) +
#     scale_linetype_manual(name = "Scenario", 
#                           values = c("Baseline" = "solid", "Intervention" = "dotted")) +
#     labs(title = "SF_12 Scores by Income Quintile",
#          subtitle = tit,
#          x = "Year",
#          y = "Mean SF_12 MCS") +
#     theme_minimal() +
#     theme(legend.position = "right",
#           legend.title = element_text(size = 12),
#           legend.text = element_text(size = 10))
#   
#   # Aggregate data
#   agg_data <- data %>%
#     mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention')) %>%
#     group_by(year, income_quintile, scenario) %>%
#     summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
#     spread(scenario, mean_SF_12) %>%
#     mutate(difference = Intervention - Baseline)
#   
#   p2 <- ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
#     geom_bar(stat = "identity", position = "dodge") +
#     scale_fill_manual(name = "Income Quintile", 
#                       values = c("red", "blue", "green", "orange", "purple")) +
#     labs(title = "Average Difference in SF_12 Scores by Income Quintile",
#          subtitle = tit,
#          x = "Year",
#          y = "Difference in SF_12 Score") +
#     theme_minimal() +
#     theme(legend.position = "right",
#           legend.title = element_text(size = 12),
#           legend.text = element_text(size = 10))
#   
#   print(p1)
#   print(p2)
# }

inequality_plots <- function(summary_group, scen) {

@@

  # Combine the data
  data_combined <- data %>%
    mutate(scenario = ifelse(scenario == 'baseline', 'Baseline', 'Intervention'))

@@

  # Aggregate data
  agg_data <- data %>%
    mutate(scenario = ifelse(scenario == 'baseline', 'Baseline', 'Intervention')) %>%
    group_by(year, income_quintile, scenario) %>%
    summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
    spread(scenario, mean_SF_12) %>%
    mutate(difference = Intervention - Baseline)

@@

```{r}
inequality_plots(summary_group = 'whole_pop',
                 scen = 'ChildPovertyReductionRELATIVE_2')
```

@@

```{r}
inequality_plots(summary_group = 'families',
                 scen = 'ChildPovertyReductionRELATIVE_2')
```

@@

```{r}
inequality_plots(summary_group = 'whole_pop',
                 scen = 'ChildPovertyReductionABSOLUTE')
```

@@

```{r}
inequality_plots(summary_group = 'families',
                 scen = 'ChildPovertyReductionABSOLUTE')
```
